Development of Performance Regression Analysis Tool using Distributed Tracing on Microservice-based Application\\

### 2022-06-23 paper.tex
txs auto checkin

K-S statistic are obtained by finding the furthest vertical distance between the two CDFs as indicated by the arrows. The greater the distance, the more likely it is that two CDFs are from two different distributions so that it can be an indication that there has been a change on performance.
\begin{figure}[htb]
	\centering
	\includegraphics[width=0.4\textwidth]{resources/ch2/ks.png}
	\caption{CDF dari dua buah sampel, panah menunjukkan nilai statistik Kolmogorov-Smirnov \cite{wiki:ks-test}}
	\label{ks-example}
\end{figure}

>>>>

K-S statistic are obtained by finding the furthest vertical distance between the two CDFs as indicated by the arrows. The greater the distance, the more likely it is that two CDFs are from two different distributions so that it can be an indication that there has been a change on performance.
\begin{figure}[htb]
	\centering
	\includegraphics[width=0.4\textwidth]{resources/ch2/ks.png}
	\caption{CDF of two samples, arrows indicate the Kolmogorov-Smirnov statistical value \cite{wiki:ks-test}}
	\label{ks-example}
\end{figure}

The Cummulative Analysis approach will be used to fullfil the first needs of the PRA system.

On the other hand, aggregation analysis can help to identify changes that not too visible on the performance of a service. When comparing two fruits
trace set, we can also see the latency contribution associated with the tag,
operations, and services and also see how these contributions change over time
time.
